Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-21 revise/revise.tex
better merge solution.

% Template article for Elsevier's document class `elsarticle'
% with numbered style bibliographic references
% SP 2008/03/01
%
%
%
% $Id: elsarticle-template-num.tex 4 2009-10-24 08:22:58Z rishi $
%
%
%\documentclass[preprint,12pt]{elsarticle}
\documentclass[answers,12pt]{exam}

@@

%\journal{Advances in Engineering Software}

@@

        \title{<++>}

@@

\section*{General Response}
I would like to thank the reviewers for their detailed assessment of this 
paper.

\section*{Reviewer 1}
\begin{questions}
\question The paper presents an interesting and original work on a new solver for MSRs based on the MOOSE platform.  It is clearly written but it lacks depth both in the description of the work and in the positioning of it in the available scientific literature.  In addition, the paper fails in properly supporting the main claim of an " unmatched fidelity in coupled neutronics and thermal hydraulics MSR simulation", since the proposed results are limited and compared only with an old MSRE model. The paper would represent an interesting contribution to the scientific community but it requires revision. In  particular the authors should deepen their bibliographical research, and include a comparison either with experimental results or with other state-of-the-art tools.
\begin{solution}
<++>
\end{solution}

\question
 In the introduction, the authors mention that:
"Two key advantages offered by the fluid-fuelled MSR are improved fuel utilization and no radiation damage constraint on attainable fuel burn-up. Together, these attributes result in significantly reduced core fissile inventories and spent nuclear fuel mass"
However, the fissile inventory is not necessarily related to fuel burnup and fuel utilization. It can actually be  very high in chloride-based fast-spectrum MSRs.
\begin{solution}
<++>
\end{solution}

@@

Other important works have been prepared in China in the frame of the Chinese MSR program.

\begin{solution}
<++>
\end{solution}

\question 
 The authors should deepen the discussion on the current state of the art, mentioning at least the several efforts spent in the Evol project, and re-balancing their claims accordingly.
\begin{solution}
<++>
\end{solution}

\question 
The authors write:
"Moltres is devoted to previously unmatched fidelity in coupled neutronics and thermal hydraulics MSR simulation."
This is an overstatement as codes with similar degree of fidelity have been written in the past. This is the case of the tools developed in the frame of the Evol project, as well as e.g. the work from Aufiero on the coupling between OpenFOAM and Serpent (that the authors mention earlier in the introduction). The authors are required to modify this sentence based on a better bibliographical research.
\begin{solution}
<++>
\end{solution}

\question 
Concerning the openness of the code and the possibility to contribute to it, it should be noted that codes solving for neutron transport can be subject to export restrictions (following their potential dual use), and in principle all contributors should get an export control authorization from their own country. The authors are not strictly required to change the manuscript, but they may consider mentioning the fact that the openness of a nuclear code can be somewhat thwarted by national and international laws.

\begin{solution}
<++>
\end{solution}

\question  It's somehow interesting that "For some three-dimensional simulations, the number of elements in the mesh and total number of degrees of freedom exceed one million and ten million respectively. To handle problems of this size, we ran Moltres on up to 608 cores." Normally problems of few million degrees of freedom can be handled with few tens of cores. The authors should discuss more extensively the performances of their code in order to give the reader the possibility to compare them with those of other tools. In particular, it is possible that slow performances may derive from trying to achieve a fully coupled solution (i.e., all the equations in the same matrix), which seems to be the case in this work. In this sense and to better support the claims of the paper, it would be important to compare the performances of a segregated and a fully coupled  solver, both in terms of accuracy and computational time. In addition to helping supporting the claims of the paper, this
would represent a significant contribution to the scientific community, since many of the currently available tools employ segregated solvers, and since the advantages and disadvantages of a fully coupled solver are often a subject of discussion.

\begin{solution}
<++>
\end{solution}

\question Are all equations solved on the same mesh? In this case, is this a strict requirement? Please clarify.

\begin{solution}
<++>
\end{solution}

\question The heat generation in the graphite is calculated as a fraction of that in the fuel. How exactly is this achieved considering that the two sources are spatially separated?

\begin{solution}
<++>
\end{solution}

\question It is not clear how the domain is discretized. Is there a radial discretization in graphite and channels? Was the mesh convergence checked? Please discuss.

\begin{solution}
<++>
\end{solution}

\question  The MSRE had Reynolds numbers very close to the laminar-turbulent transition. Did you use a laminar model? In case, did you encounter convergence problems ?
Or did you include turbulence? More generally, is Moltres capable of turbulent simulations?

\begin{solution}
<++>
\end{solution}

\question The authors are required to use the international system of units (meters, Kelvin, etc).

\begin{solution}
<++>
\end{solution}

\question The authors should briefly describe what "MSRE design models" are. Otherwise it is very difficult for the readers to assess the accuracy of the model.

\begin{solution}
<++>
\end{solution}

\question  Is the heat generation in the hottest channel the same for the Moltres and the MSRE model?

\begin{solution}
<++>
\end{solution}

\question  The authors claim an unprecedented accuracy of their model? How the results of their model compare with previous results from other authors? The presented results do not seem sufficient to support such claim.

\begin{solution}
<++>
\end{solution}

\question The differences between the MSRE and the Moltres model are significant and should be discussed in more details. In particular the difference between fast fluxes is suspicious.

\begin{solution}
<++>
\end{solution}

\question The proposed scaling test is very limited. Proper scaling tests would require weak and strong scaling tests, an assessment on the impact of the size of problem per core, a separate assessment of intra-node and extra-node scaling, etc. In addition, information should be provided on the employed numerical algorithms and on the parallelization strategy. The authors should either extend significantly the section, or remove it completely.

\begin{solution}
<++>
\end{solution}
\end{questions}
\end{document}  
  %
  % End of file `elsarticle-template-num.tex'.

>>>>

% Template article for Elsevier's document class `elsarticle'
% with numbered style bibliographic references
% SP 2008/03/01
%
%
%
% $Id: elsarticle-template-num.tex 4 2009-10-24 08:22:58Z rishi $
%
%
%\documentclass[preprint,12pt]{elsarticle}
\documentclass[answers,11pt]{exam}

@@

%\journal{Annals of Nuclear Energy}

@@

\title{Introduction to Moltres: an Application for Simulation of Molten Salt 
        Reactors}

@@

\section*{Review General Response}
We would like to again thank the reviewers for their detailed assessment of 
this paper.

\section*{Reviewer 1}
\begin{questions}

\question The paper presents an interesting and original work on a new solver
for MSRs based on the MOOSE platform.  It is clearly written but it lacks depth
both in the description of the work and in the positioning of it in the
available scientific literature.  In addition, the paper fails in properly
supporting the main claim of an ``unmatched fidelity in coupled neutronics and
thermal hydraulics MSR simulation'', since the proposed results are limited and
compared only with an old MSRE model. The paper would represent an interesting
contribution to the scientific community but it requires revision. In
particular the authors should deepen their bibliographical research, and
include a comparison either with experimental results or with other
state-of-the-art tools.
\begin{solution}
        The statement concerning `unmatched' fidelity has been removed 
        entirely.
\end{solution}

\question <++>

\question In the introduction, the authors mention that:
``Two key advantages offered by the fluid-fuelled MSR are improved fuel 
        utilization and no radiation damage constraint on attainable fuel 
        burn-up. Together, these attributes result in significantly reduced 
        core fissile inventories and spent nuclear fuel mass''
However, the fissile inventory is not necessarily related to fuel burnup and fuel utilization. It can actually be  very high in chloride-based fast-spectrum MSRs.
\begin{solution}
        <++>
\end{solution}

@@

Other important works have been prepared in China in the frame of the Chinese MSR program.
\begin{solution}
        <++>
\end{solution}

\question The authors should deepen the discussion on the current state of the art, mentioning at least the several efforts spent in the Evol project, and re-balancing their claims accordingly.

\question The authors write:
``Moltres is devoted to previously unmatched fidelity in coupled neutronics and 
        thermal hydraulics MSR simulation.''
This is an overstatement as codes with similar degree of fidelity have been written in the past. This is the case of the tools developed in the frame of the Evol project, as well as e.g. the work from Aufiero on the coupling between OpenFOAM and Serpent (that the authors mention earlier in the introduction). The authors are required to modify this sentence based on a better bibliographical research.
\begin{solution}
        <++>
\end{solution}

\question Concerning the openness of the code and the possibility to contribute to it, it should be noted that codes solving for neutron transport can be subject to export restrictions (following their potential dual use), and in principle all contributors should get an export control authorization from their own country. The authors are not strictly required to change the manuscript, but they may consider mentioning the fact that the openness of a nuclear code can be somewhat thwarted by national and international laws.
\begin{solution}
        <++>
\end{solution}

\question It's somehow interesting that ``For some three-dimensional 
simulations, the number of elements in the mesh and total number of degrees of 
freedom exceed one million and ten million respectively. To handle problems of 
this size, we ran Moltres on up to 608 cores.'' Normally problems of few million degrees of freedom can be handled with few tens of cores. The authors should discuss more extensively the performances of their code in order to give the reader the possibility to compare them with those of other tools. In particular, it is possible that slow performances may derive from trying to achieve a fully coupled solution (i.e., all the equations in the same matrix), which seems to be the case in this work. In this sense and to better support the claims of the paper, it would be important to compare the performances of a segregated and a fully coupled  solver, both in terms of accuracy and computational time. In addition to helping supporting the claims of the paper, this
would represent a significant contribution to the scientific community, since many of the currently available tools employ segregated solvers, and since the advantages and disadvantages of a fully coupled solver are often a subject of discussion.
\begin{solution}
        <++>
\end{solution}

\question Are all equations solved on the same mesh? In this case, is this a strict requirement? Please clarify.
\begin{solution}
        <++>
\end{solution}

\question The heat generation in the graphite is calculated as a fraction of that in the fuel. How exactly is this achieved considering that the two sources are spatially separated?
\begin{solution}
        <++>
\end{solution}

\question It is not clear how the domain is discretized. Is there a radial discretization in graphite and channels? Was the mesh convergence checked? Please discuss.
\begin{solution}
        <++>
\end{solution}

\question The MSRE had Reynolds numbers very close to the laminar-turbulent transition. Did you use a laminar model? In case, did you encounter convergence problems ?
Or did you include turbulence? More generally, is Moltres capable of turbulent simulations?
\begin{solution}
        <++>
\end{solution}

\question The authors are required to use the international system of units (meters, Kelvin, etc).
\begin{solution}
        <++>
\end{solution}

\question The authors should briefly describe what ``MSRE design models'' are. Otherwise it is very difficult for the readers to assess the accuracy of the model.
\begin{solution}
        <++>
\end{solution}

\question Is the heat generation in the hottest channel the same for the Moltres and the MSRE model?
\begin{solution}
        <++>
\end{solution}

\question The authors claim an unprecedented accuracy of their model? How the results of their model compare with previous results from other authors? The presented results do not seem sufficient to support such claim.
\begin{solution}
        <++>
\end{solution}

\question The differences between the MSRE and the Moltres model are significant and should be discussed in more details. In particular the difference between fast fluxes is suspicious.
\begin{solution}
        <++>
\end{solution}

\question The proposed scaling test is very limited. Proper scaling tests would require weak and strong scaling tests, an assessment on the impact of the size of problem per core, a separate assessment of intra-node and extra-node scaling, etc. In addition, information should be provided on the employed numerical algorithms and on the parallelization strategy. The authors should either extend significantly the section, or remove it completely.
\begin{solution}
        <++>
\end{solution}

\end{questions}
  \end{document}

  %
  % End of file `elsarticle-template-num.tex'.
